---
title: "MGEC11 Assignment 2"
author: "Xinrui Wang,1004741078"
date: "2021/6/24"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q1 
a) yi = 3 + 5 × xi + epsilon_i  where xi is U(0, 5)

```{r}
sim_1 = function(sample_size = 30) {
  x = runif(n=sample_size)*5
  y = 3 + 5 * x + rnorm(n = sample_size, mean = 0, sd = sqrt(2))
  data.frame(x, y)
}

set.seed(42)
sim_data_1 = sim_1()
head(sim_data_1)

plot(y ~ x, data = sim_data_1, col = "grey", pch = 20,
     main = "LR Model: yi = 3 + 5 × xi + e_i, n=30")
fit_1 = lm(y ~ x, data = sim_data_1)
abline(fit_1, col = "darkorange", lwd = 3)
```
b)sim for n=100,150,500
```{r}
sim_2 = function(sample_size = 100) {
  x = runif(n=sample_size)*5
  y = 3 + 5 * x + rnorm(n = sample_size, mean = 0, sd = sqrt(2))
  data.frame(x, y)
}

set.seed(42)
sim_data_2 = sim_2()
head(sim_data_2)

plot(y ~ x, data = sim_data_2, col = "grey", pch = 20,
     main = "LR Model: yi = 3 + 5 × xi + e_i, n=100")
fit_2 = lm(y ~ x, data = sim_data_2)
abline(fit_2, col = "darkorange", lwd = 3)
```

```{r}
sim_3 = function(sample_size = 150) {
  x = runif(n=sample_size)*5
  y = 3 + 5 * x + rnorm(n = sample_size, mean = 0, sd = sqrt(2))
  data.frame(x, y)
}

set.seed(42)
sim_data_3 = sim_3()
head(sim_data_3)

plot(y ~ x, data = sim_data_3, col = "grey", pch = 20,
     main = "LR Model: yi = 3 + 5 × xi + e_i, n=150")
fit_3 = lm(y ~ x, data = sim_data_3)
abline(fit_3, col = "darkorange", lwd = 3)
```

```{r}
sim_4 = function(sample_size = 500) {
  x = runif(n=sample_size)*5
  y = 3 + 5 * x + rnorm(n = sample_size, mean = 0, sd = sqrt(2))
  data.frame(x, y)
}

set.seed(42)
sim_data_4 = sim_4()
head(sim_data_4)

plot(y ~ x, data = sim_data_4, col = "grey", pch = 20,
     main = "LR Model: yi = 3 + 5 × xi + e_i, n=500")
fit_4 = lm(y ~ x, data = sim_data_4)
abline(fit_4, col = "darkorange", lwd = 3)
```


get coef:
```{r}
coef(fit_1)
coef(fit_2)
coef(fit_3)
coef(fit_4)
```
The true value is intercept = 3 and slope = 5. From the results, as sample size n increases, the estimated slope becomes more accurate, ie. it is closer and closer to the true slope 5.


## Q2

```{r}
data<-read.csv("C:/Users/69544/Desktop/MGEC11/A2/data1.csv", header = T)
model<-lm(y~cbind(x1,x2),data = data)
par(mfrow = c(2, 2))
plot(model)
```
From the residuals vs fitted figure, we don't have a horizontal line, the linearity is violated. also, we can see there is a pattern in the residuals, they first increase and then decrease. Thus, the model is not fit because the residuals do not distribute evenly. 
Considering the normal Q-Q plot, we get heavy tails and residuals points don't follow the line very well, so normality is violated. 
Since the residuals moves from far to close to the linear model and move from close to far, we guess the model should be y=√x  or y=lnx whose derivative becomes smaller when x becomes larger.
Therefore, the model seems not appropriate.


```{r}
model2<- lm(y~log10(x1)+log10(x2),data=data)
par(mfrow = c(2, 2))
plot(model2)
summary(model)
```
```{r}
library(lmtest)
bptest(model)
bptest(model2)
```
we see a large p-value, so we do not reject the null of homoscedasticity.
