---
title: "A1 R Markdown"
author: "Xinrui Wang 1004741078, Hanjun Ge 1005719741"
date: "2021/9/15"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Question 1

### Part A

The theoretical sampling distribution of $\overline{y}$ is normal distribution, $\overline{y} \sim \text{Normal}(\mu = 60, \sigma = 2)$.\
The theoretical sampling distribution of $X^{2}$ is Chi-square distribution with $df = 25 - 1 = 24$.\
The theoretical sampling distribution of $t$ is normal distribution, $\overline{y} \sim \text{Normal}(\mu = 0, \sigma = 1)$.\

### Part B

```{r}

set.seed(1005719741)
n = 25
mu = 60
sigma = 10
yba_list = list()
s_list = list()
x2_list = list()
t_list = list()


for (i in 1:10000) {
  sample = rnorm(n = 25, mean = 60, sd = 10)
  yba_list[i] = mean(sample)
  s_list[i] = sd(sample)
  x2_list[i] = (n-1) * var(sample) / (sigma^2)
  t_list[i] = (mean(sample) - mu) / (sd(sample) / sqrt(n))
}


hist(as.numeric(yba_list),
     main = "Yba Histogram",
     xlab = "Yba",
     breaks = 15
)

plot(density(as.numeric(yba_list)), main = "Yba Histogram Theoretical Density", col = "red")

hist(as.numeric(x2_list),
     main = "X2 Histogram",
     xlab = "X2",
     breaks = 15
)

plot(density(as.numeric(x2_list)), main = "X2 Histogram Theoretical Density", col = "red")

hist(as.numeric(t_list),
     main = "t Histogram",
     xlab = "t",
     breaks = 15
)

plot(density(as.numeric(t_list)), main = "t Histogram Theoretical Density", col = "red")

```

### Part C

```{r}

yba_list_mean = mean(as.numeric(yba_list))
yba_list_sd = sd(as.numeric(yba_list))
yba_list_percentile = quantile(as.numeric(yba_list),c(0.025,0.25,0.50,0.75,0.975))

x2_list_mean = mean(as.numeric(x2_list))
x2_list_sd = sd(as.numeric(x2_list))
x2_list_percentile = quantile(as.numeric(x2_list),c(0.025,0.25,0.50,0.75,0.975))
     
t_list_mean = mean(as.numeric(t_list))
t_list_sd = sd(as.numeric(t_list))
t_list_percentile = quantile(as.numeric(t_list),c(0.025,0.25,0.50,0.75,0.975))

yba_list_mean
yba_list_sd
yba_list_percentile

x2_list_mean
x2_list_sd
x2_list_percentile

t_list_mean
t_list_sd
t_list_percentile

```

Comment: R output is very close to the theoretical values stated in part a. For $\overline{y}$, 60.00261 and 2.008066 are close to 60 and 2. For $t$, 0.0006309305 and 1.050759 are close to 0 and 1. $X^{2}$ distribution here is very close to a normal distribution since the degree of freedom 24 is large.

## Question 2

### Part A

``` {r}

NHLhtwt = read.csv("NHLhtwt.csv", header = TRUE)

plot(NHLhtwt$Height, NHLhtwt$Weight, xlab = "Height, in inches", ylab = "Weight, in pounds")

```

Comment: We can see from the scatter plot that weight and height has a positive correlation.

### Part B
``` {r}

model = lm(Weight ~ Height, data = NHLhtwt)

summary(model)

```


### Part C

The regression coefficient test $H_0$: $\hat{\beta_{1}}\ \le 0$ vs $H_a$: $\hat{\beta_{1}}\ > 0$. Here, $p$-value is very small (<2$e$-16) compared to 0.01. Therefore, it is statistically significant. We can conclude that here is a positive association between weight and height using the regression coefficient.

### Part D
``` {r}

confint(model, level = 0.95)

```

\
\
\
Thank you for reviewing.\
The code below is for the calculation of question 4 and 5.\
Please refer to the handwritten document.\


## Question 4

### Part A

```{r}

n = 30                
Xba = 41.92
Yba = 35.83
Sxx = 2207.45
Syy = 654.86
Sxy = 658.37

Beta1_hat <- Sxy / Sxx
Beta0_hat <- Yba - Xba * Beta1_hat

Beta1_hat
Beta0_hat

```

### Part B

``` {r}

SSE <- Syy - Beta1_hat * Sxy
SE_Beta1_hat <- sqrt(SSE / Sxx / (n-2))
SE_Beta0_hat <- sqrt(1/n + Xba ^ 2 / Sxx) * sqrt(SSE / (n-2))

SE_Beta1_hat
SE_Beta0_hat

```

### Part C

``` {r}

alpha = 1 - 0.95

CI_left_Beta0_hat <- Beta0_hat - qt(1 - alpha/2, n - 2) * SE_Beta0_hat
CI_right_Beta0_hat <- Beta0_hat + qt(1 - alpha/2, n - 2) * SE_Beta0_hat

CI_left_Beta1_hat <- Beta1_hat - qt(1 - alpha/2, n - 2) * SE_Beta1_hat
CI_right_Beta1_hat <- Beta1_hat + qt(1 - alpha/2, n - 2) * SE_Beta1_hat

CI_left_Beta0_hat
CI_right_Beta0_hat

CI_left_Beta1_hat
CI_right_Beta1_hat

```


## Question 5

### Part E

```{r}

X = c(7, 12, 4, 14, 25, 30)
Y = c(128, 213, 75, 250, 446, 540)

XY = sum(X * Y)
Xsquare = sum(X * X)

Beta1_hat_Q5 = XY / Xsquare

XY
Xsquare
Beta1_hat_Q5

Model_Q5 = lm(Y ~ X)
plot(X,Y, xlab = "X axis", ylab = "Y axis")
lines(X,Y, lwd = 2, col = "red")
summary(Model_Q5)

```


